---
title: "Question about MEM"
author: "Yu'an Yang"
output: html_notebook
---
The data is an experiment I did with Mandarin-speaking three-year-olds. The study is a modified version of Truth Value Judgment Task. Instead of saying true/false, the kids have to decide whether they need to answer to a wh-question or respond to a declarative.

```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(viridis)
library(lme4)
# The palette with grey:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#BBDFCE")

# The palette with black:
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

yy_data <- read.csv("/Users/ceshi/Documents/Work/Rscripts/Multi_level_models/group_session/random-effect-simulation-assignment-1-Yu-an/yu-an-question/data.csv")
```

The dependent variable is "yn", whether the response from participant contains a 'yes/no' marker. The independent varialbe is "dou" (whether the test sentence has a morpheme "dou") and "some_all", whether the scenario in a story is a "some" scenario, or a "all" scenario. 

So I plotted "some_all" and "dou":
```{r plot}
df_dou <- yy_data %>%
 group_by(participant, dou, some_all, age_group) %>% 
  summarize(proportion = mean(yn)) %>% 
  group_by(dou, age_group, some_all) %>% 
  summarise(avg_prop = mean(proportion), sd=sd(proportion), n=n()) %>% 
  mutate(SEM = sd/sqrt(n),upper=avg_prop+SEM, lower= avg_prop-SEM)
df_dou$dou <- as.factor(df_dou$dou)
df_dou$some_all <- as.factor(df_dou$some_all)
label_facet <- c("0" ="adults", "1" = "children")
pdou<- ggplot(df_dou, aes(x=dou, y=avg_prop, fill = some_all))+
  geom_bar(stat="identity", position = position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), stat = "identity", width = 0.2, position=position_dodge(0.9)) +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
  labs(y = '% yes/no-responses', x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
 # scale_x_discrete(labels=c("+Dou","-Dou")) +
 # scale_fill_manual(values=cbPalette[c(2,5)], name = "Scenario", breaks=c(1, 0), labels=c("all", "some")) +
  theme_bw()

pdou
```

So when I run the model, there's a warning "isSingular", and I'm not sure what it entails:
```{r stats}
mdou_pol1 <- glmer(formula = yn ~ dou*some_all +age_group+ (1|participant) +(1|test_number), family = binomial, data = yy_data)
summary(mdou_pol1)
print(mdou_pol1)
```

